---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r dingo}
unzip("activity.zip")
data <- read.csv("activity.csv")




```

text




## What is mean total number of steps taken per day?
```{r dingo2}
dailyData <- aggregate(steps~date, data, sum, na.rm=TRUE)
hist(dailyData$steps)

a <- mean(dailyData$steps, na.rm=TRUE)
b <- median(dailyData$steps, na.rm=TRUE)



```

Mean is `r as.integer(a)`, median is `r b`.





## What is the average daily activity pattern?

```{r dingo3}

intervalAgg <- aggregate(steps~interval, data, sum, na.rm=TRUE)

plot(intervalAgg$interval,  intervalAgg$steps, type="l")


intervalue<- subset(intervalAgg, intervalAgg$steps == max(intervalAgg$steps, na.rm=TRUE))$interval

intervalue


```

text




## Imputing missing values

```{r dingo4}
navals <- sum(is.na(data$steps))
navals

newData <- data

interVals <- unique(newData$interval)


#sorry for this garbage, recovering java programmer

for(i in 1:length(interVals)){
        #print(interVals[i])
        subByInt <- subset(newData, newData$interval == interVals[i])
        #print(subByInt)
        mean <- mean(subByInt$steps, na.rm=TRUE)
        #if(dim(subByInt)[1]=="0"){next} 
        if(is.nan(mean)){mean<-0} #all na values inthis interval
        print(nrow(subByInt))
        for(j in 1:nrow(subByInt)){
               if(is.na(newData$steps[j])){
                   newData$steps[j] <- mean #replaces NA with interval mean
                
               } 
        subByInt <- NA        
        }
} #end of cleaning NA steps

newDailyData <- aggregate(steps~date, newData, sum, na.rm=TRUE)
hist(newDailyData$steps)

c <- mean(dailyData$steps, na.rm=TRUE)
d <- median(dailyData$steps, na.rm=TRUE)

print(c(c,d))




```

Seems like no impact?





## Are there differences in activity patterns between weekdays and weekends?
```{r dingo5}





```

text





yeet
yeet
yeet
yeet

yeet
yeet
yeet
yeet
yeet
yeet
yeet
yeet

yeet
yeet
yeet
yeet


yeet


yeet

yeet


yeet
yeet
yeet
yeet
